Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-11-17 poster.tex
TikZ poster finished!

\usepackage{etoolbox}
\makeatletter
\patchcmd{\beamer@@tmpl@headline}{wd=47in}{wd=75in}{}{}
\makeatother

@@

\begin{document}
\addtobeamertemplate{headline}{} 
{\begin{tikzpicture}[remember picture, overlay]
     \node [anchor=north east, inner sep=3cm]  at (current page.north east)
           {\includegraphics[height=7cm]{figures/csail.png}};
                \node [anchor=north west, inner sep=3cm]  at (current page.north west)
     {\includegraphics[height=5cm]{figures/bcs.png}};
\end{tikzpicture}}

@@

\begin{block}{Two-Stage Pipeline}
\hspace{-5cm}  \includegraphics[width = 50cm]{pipeline.pdf}

@@

\begin{block}{Parsing Images into Drawing Commands (specs)}
\vspace{-3cm}  \includegraphics[width = 40cm]{architecture.pdf}

%\begin{figure}[h]\centering
  \begin{minipage}[c]{0.49\textwidth} 
    \centering  \includegraphics[width = \textwidth]{figures/drawingAccuracy.png}            \vspace{-0.5cm} 
  \end{minipage}\hfill%
      \begin{minipage}[c]{0.5\textwidth} 
  {\small (Left) NN outputs vs ground truth on hand drawings (measured by IoU), as we consider larger sets of samples (1, 5, 100).
     (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth. Red: the full model. Other colors: ablations. Model is at ceiling for synthetic $\LaTeX$ output.}
      \end{minipage}

%\end{figure}
\end{block}

@@

@@

@@

\includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}

Time to synthesize a minimum cost program. Sketch: out-of-the-box performance of Sketch. DC: Deep--Coder style baseline that predicts program components, trained like Balog 2016. Oracle:  upper bounds  the performance of any bias--optimal search policy. $\infty = $ timeout. Red dashed line is median time
  \end{block}

    \vspace{2cm}
    \begin{figure}
        \includegraphics[width = 0.6\textwidth]{figures/programSuccess7.png}\hfill
  \includegraphics[width = 0.6\textwidth]{figures/programSuccess16.png}
  \caption{Left: hand drawings. Center: interpretations favored by the deep network. Right: interpretations favored after learning a prior over programs. The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}
      \end{figure}
    \end{block}

@@

>>>>

\usepackage{etoolbox}
\makeatletter
\patchcmd{\beamer@@tmpl@headline}{wd=47in}{wd=95in}{}{}
\makeatother

@@

\begin{document}
\addtobeamertemplate{headline}{} 
{\begin{tikzpicture}[remember picture, overlay]
     \node [anchor=north east, inner sep=3cm]  at ([yshift=2cm]current page.north east)
           {\includegraphics[height=10cm]{figures/Brown.png}};
                \node [anchor=north west, inner sep=3cm]  at (current page.north west)
     {\includegraphics[height=7cm]{figures/csail.png}};
\end{tikzpicture}}

@@

      \begin{alertblock}{\red Acknowledgments}
         We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
\#1753684, the MUSE program (DARPA grant FA8750-14-2-0242),
and AFOSR award FA9550-16-1-0012.
        \end{alertblock}

@@

@@

  \begin{block}{Two-Stage Pipeline}
\centering  \includegraphics[width = 80cm]{pipeline.pdf}

@@

\begin{block}{Parsing Images into Drawing Commands (specs)}
\hspace{10cm}  \includegraphics[width = 40cm]{architecture.pdf}

\end{block}

\begin{block}{Generalizing to real hand drawings}
  \textbf{  Train on simulated noisy data (left) \& learn distance metric between images (right)}\\
  \newcommand{\noisySize}{0.2\textwidth}
  \begin{minipage}[t]{\noisySize}
    \centering\includegraphics[width = \textwidth]{figures/expert-60-reduced.png}\\
{\small     (a): hand drawing}
  \end{minipage}%
  \begin{minipage}[t]{\noisySize}
    \centering\includegraphics[width = \textwidth]{figures/60-1-reduced.png}\\
{\small     (b): noisy render of (a)}
  \end{minipage}\hfill%
  \begin{minipage}[t]{0.5\textwidth}\vspace{-9cm}
    \textbf{Learned distance metric}\\
    Serves as likelihood surrogate for SMC
      \begin{align*}
    -\log L_{\text{learned}}(\text{render}&(S_1)|\text{render}(S_2))\approx\\& |S_1 - S_2| + |S_2 - S_1|\label{symmetricDistance}
      \end{align*}
      $S_1$: noisy render of random scene\\
      $S_2$: nonnoisy render of random scene
  \end{minipage}%

  \vspace{3cm}

    \begin{minipage}[c]{0.49\textwidth} 
    \centering  \includegraphics[width = \textwidth]{figures/drawingAccuracy.png}            \vspace{-0.5cm} 
  \end{minipage}\hfill%
      \begin{minipage}[c]{0.5\textwidth} 
  {\small (Left) NN outputs vs ground truth on hand drawings (measured by IoU), as we consider larger sets of samples (1, 5, 100).
     (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth. Red: the full model. Other colors: ablations. Model is at ceiling for synthetic $\LaTeX$ output.}
      \end{minipage}

  \end{block}

@@

\begin{flushright}
  Experimental results on synthesis policy: See lower right of poster
  \end{flushright}

  \end{block}

@@

    \vspace{2cm}
    \begin{figure}
        \includegraphics[width = 0.5\textwidth]{figures/programSuccess7.png}\\
  \includegraphics[width = 0.5\textwidth]{figures/programSuccess16.png}
  \caption{Left: hand drawings. Center: interpretations favored by the deep network. Right: interpretations favored after learning a prior over programs. The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}
    \end{figure}
\vspace{-1cm}
  \end{block}

  \begin{block}{Synthesis times}    
    \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}

{\small Time to synthesize a minimum cost program. Sketch: out-of-the-box performance of Sketch. DC: Deep--Coder style baseline that predicts program components, trained like Balog 2016. Oracle:  upper bounds  the performance of any bias--optimal search policy. $\infty = $ timeout. Red dashed line is median time}
    \end{block}
